Motmot: A Distributed Chat Protocol

### 2012-05-04 paper/paper.tex
updated status report in paper

The input listener listens for input from the discovery server. Upon receiving a
message it deserializes the message from the message pack buffer, finds the
opcode, and calls the appropriate \libpurple functions based on the opcode and
the rest of the data sent by the message. Writes to the discovery server are
handled in individual purple functions. Based on the user action, a message pack
object is created, and the data is sent to the server across the connection.
Messages are asynchronous.

@@

>>>>

The input listener listens for input from the discovery server. Upon receiving a
message it deserializes the message from the message pack buffer, finds the
opcode, and calls the appropriate \libpurple functions based on the opcode and
the rest of the data sent by the message. Writes to the discovery server are
handled in individual purple functions. Based on the user action, a message pack
object is created, and the data is sent to the server across the connection.
Messages are asynchronous. Status updates also include the address and port
of a user so the client can know the location of a user to connect to.

The code to interact with the discovery server currently has a bug involving
status updates after accepting a friend request.

@@

We were unable to fully integrate the \libmotmot protocol in the plugin.
The code is outlined with in the plugin file, however it is not currently
functional. Hopefully this will be fixed in future versions so that
\libmotmot can be used as a \libpurple plugin.
